Transfer Learning in Visual and Relational Reasoning

### 2020-03-02 Transfer_Learning/eccv_submission/eccv_paper_main.tex
Add Paper ID and slight clean up.

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCVSubNumber{100}  % Insert your submission number here

\title{Transfer Learning in Visual and Relational Reasoning} % Replace with your title

@@

\begin{comment}
\author{T.S. Jayram\inst{1} \and  Vincent Marois\inst{2} \and Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center} \and Tomasz Kornuta\inst{3}  \and Emre Sevgen\samethanks \and Ahmet Ozcan\inst{1}}

\institute{IBM Research AI, Almaden Research Center, San Jose, CA, USA\\ \email{\{jayram,  asozcan\}@us.ibm.com}
      \and IBM Research AI, Thomas J. Watson Research Center, York Town, NY, USA\\ \email{vincent.marois@ibm.com}
      \and NVIDIA, Santa Clara, CA, USA\\ \email{tkornuta@nvidia.com}}
\end{comment}
%******************

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
\end{comment}
%******************
\maketitle

@@

\clearpage
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{../bibliography}
\end{document}

>>>>

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCVSubNumber{7169}

\title{Transfer Learning in Visual and Relational Reasoning}

@@

% CAMERA READY SUBMISSION
\begin{comment}
\author{T.S. Jayram\inst{1} \and  Vincent Marois\inst{2} \and Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center} \and Tomasz Kornuta\inst{3} \and Ahmet Ozcan\inst{1}}

\authorrunning{T.S. Jayram et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.

\institute{IBM Research AI, Almaden Research Center, San Jose, CA, USA\\ \email{\{jayram,  asozcan\}@us.ibm.com}
      \and IBM Research AI, Thomas J. Watson Research Center, York Town, NY, USA\\ \email{vincent.marois@ibm.com}
      \and NVIDIA, Santa Clara, CA, USA\\ \email{tkornuta@nvidia.com}}
\end{comment}
%******************
\maketitle

@@

\clearpage
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
\bibliographystyle{splncs04}
\bibliography{../bibliography}
\end{document}
